ICS_Cytokine_Analysis

### 2019-06-10 Cytokine_Analysis.Rmd
Took PMA out to put in HC script

```{r source}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
```

@@

CD4<-plot_filter(read.csv("ICS_CD4_Cytokine_clean.csv"))

@@

data<-read.csv("ICS_Donor_Info_clean.csv")
data$TB<-gsub("BCG|Unknown", "Naïve", data$TB)
data$TB<-factor(data$TB, levels=c("Naïve","Healthy Control","LTBI","Active TB"))
data$SM<-gsub("US|Not US|Unknown", "Naïve", data$SM)
data$SM<-factor(data$SM, levels=c("Naïve","Negative","Schisto+"))
Donor<-data
```
#P-values for Cytokine Comparisons

##PMA & Ionomycin
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PMA") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##Whole Cell Lysate
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="WCL") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##CFP-10 & ESAT-6
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

### PMA
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
####WCL
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("\\.", "+", col)
    name<-gsub("Freq","", name)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}

### PEP
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("\\.", "+", col)
    name<-gsub("Freq","", name)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
```

@@

### PMA
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             title="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
####WCL
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}

### PEP
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(name, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
```

>>>>

```{r source}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")
```

@@

CD4<-plot_filter(read.csv("ICS_CD4_Cytokine_clean.csv"))
CD4b<-plot_filter(read.csv("ICS_Cytokine_new.csv"))

@@

data<-read.csv("ICS_Donor_Info_clean.csv")
data$TB<-gsub("BCG|Unknown", "Naïve", data$TB)
data$TB<-factor(data$TB, levels=c("Naïve","Healthy Control","LTBI","Active TB"))
data$SM<-gsub("US|Not US|Unknown", "Naïve", data$SM)
data$SM<-factor(data$SM, levels=c("Naïve","Negative","Schisto+"))
Donor<-data
```

##PMA & Ionomycin
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PMA") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##Whole Cell Lysate
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="WCL") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
colnames<-c("TH1_total", "TH2_total")
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4b, CD4b$Stim=="WCL") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##CFP-10 & ESAT-6
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
colnames<-c("TH1_total", "TH2_total")
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4b, CD4b$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

@@

### PMA
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PMA & Ionomycin",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
####WCL
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("\\.", "+", col)
    name<-gsub("Freq","", name)
    y<-plot_with_all_stats(CD4, "WCL", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="WCL",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}

### PEP
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("\\.", "+", col)
    name<-gsub("Freq","", name)
    y<-plot_with_all_stats(CD4, "PEP", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PEP",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
```

@@

### PMA
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             title="PMA & Ionomycin",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
####WCL
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "WCL", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="WCL",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}

### PEP
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4, "WCL", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             subtitle="PEP",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
```

```{r}
library(dplyr)
library(reshape2)
library(ggplot2)
library(knitr)

colnames<-c("TH1_Total" , "TH2_Total" )

### PMA
for(col in colnames){#this will loop through each character string in the list
    #inserts each character string into the column argument of the pvals function written above
    name<-gsub("_", "+", col)
    y<-plot_with_all_stats(CD4b, "PMA", col)+
        labs(title=paste("Frequency of ", name, "+ CD4+ T cells"), 
             title="PMA & Ionomycin",
             x="",
             y=paste(col, "+ CD4+ T cells (%)"))
    print(y) #will return the output for each character string in the loop
}
```
